Multi-reference pangenome graphs

### 2022-01-09 manuscript/fig_from_alignment_to_variation_graph.tex
bugfix
figure1

\vspace{-1em}
\begin{figure}[ht!]
%  \centering
   \includegraphics[width=\linewidth]{fig_induction.pdf}
   \caption{
   A visual description of variation graph induction.
   At top, the alignment graph model.
   %   At bottom, a sequence graph obtained by contracting

   %   At top, three sequences (text1, text2, text3) 
    }
    %{\includegraphics[width=\linewidth]{fig/OUP_First_SBk_Bot_8401}} %\includegraphics[width=5cm]{name}}
    %\caption{Performance evaluation of \textit{odgi build} when translating a 90-haplotype graph of human chromosome 6 into ODGI's native format.}
\end{figure}
\vspace{-1em}

>>>>

\vspace{-1em}
\begin{figure}[ht!]
%  \centering
   \includegraphics[width=\linewidth]{fig_induction.pdf}
   \caption{
   A visual description of variation graph induction.
   \textit{Top}: an alignment graph model for three sequences and their alignments.
   Nodes are single characters (DNA base pairs, of which the forward strand is shown) in individual sequences.
   Solid ``precedence'' edges link successive characters in each sequence, and are colored (red, green, blue) to identify each.
   Dashed edges indicate aligned pairs of characters.
    \textit{Bottom}: a variation graph model induced from the alignment graph.
   %   We transform the alignment graph into a variation graph  first condensing sets of nodes in the alignment graph that are transitively linked by alignment edges.
   Each transitive match closure (gray shaded edges, of increasing darkness) in the alignment graph results in a single node in the output graph, which is labeled by the rank of the transitive closure operation that produced it.
   By recording the full set of match closures, we can project the sequences in the input through to paths in the variation graph (colored edges).
   The unique set of node pairings in the paths provide the edges of the output graph.
   %   Black nodes are numbered by the rank of the transitive closure operation
   %   At bottom, a sequence graph obtained by contracting 
   %   At top, three sequences (text1, text2, text3) 
    }
    %{\includegraphics[width=\linewidth]{fig/OUP_First_SBk_Bot_8401}} %\includegraphics[width=5cm]{name}}
    %\caption{Performance evaluation of \textit{odgi build} when translating a 90-haplotype graph of human chromosome 6 into ODGI's native format.}
\end{figure}
\vspace{-1em}
